% !TEX program = xelatex

\documentclass{resume}

%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Page number:
%\usepackage{lastpage}
%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\renewcommand{\headrulewidth}{0pt}
%\fancyhead{}
%\cfoot{\thepage\ of \pageref{LastPage}}


\begin{document}
\pagenumbering{gobble} % suppress displaying page number


\name{Your name}

\basicInfo{
  \email{yourname@gmail.com} \textperiodcentered\ 
  \phone{(+999) 12345678} \textperiodcentered\ 
  \linkedin{YourLinkedin}\textperiodcentered\ 
  \github{YourGithub}
  }
\basicInfo{
  \address{This, is, your, address}\textperiodcentered\ 
  \homepage{www.xx.site}
  }
\section{ Education}
\subsectionnoit{\textbf{Southeast University (SEU)}}{Nanjing, China}
\datedline{\textit{B.E.} in Information Engineering}{Jun, 2019}
\begin{itemize}
\item Overall GPA: 1.23/4.00 (45.67/100.00)
\item Outstanding Graduate of Southeast University (top 5\%)
\end{itemize}

%\begin{tabular}{l l l l l}
% & C\# & T-SQL & Javascript & HTML \\
% & XML & JSON & SOAP & REST
%\end{tabular}

\section{ Projects}

\bdatedsubsection{\textbf{For this project}}{Mar -- May, 2019}
\begin{itemize}[label={-}]
  \item Implemented xxx feature, in Electronics Engineering.
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\bdatedsubsection{\textbf{Resumes from undergraduate students }}{Sep -- Oct, 2018}
\begin{itemize}[label={-}]
  \item It is to your benefit to include a resume in a universal format (ASCII, PDF) whenever you contact a professor. 
  \item Many professors will not open Word attachments. 
  \item It is also to your benefit to include a copy of your resume in your application for graduate study. 
  \item Resumes from undergraduate students or recent BS graduates should be no longer than one page when formatted using an 11-pt font. 
\end{itemize}


\bdatedsubsection{\textbf{For people with archived publications }}{Mar -- Apr, 2018}
\begin{itemize}[label={-}]
  \item resumes should be limited to two pages when using an 11-pt font.
  \item and/or significant full-time work experience
\end{itemize}

\bdatedsubsection{\textbf{The resume should include the following information}}{Sep -- Nov, 2017}
\begin{itemize}[label={-}]
  \item Educational information: For each degree received or currently enrolled in
  \item please give the degree, institution name, institution city, institute state/province, and date (or expected date) of graduation
  \item List electives that you've taken, you're taking this semester, and you're planning to take next semester. 
\end{itemize}

\bdatedsubsection{\textbf{Name, mailing address, phone, and e-mail address}}{Mar -- Oct, 2016}
\begin{itemize}[label={-}]
  \item Educational information: For each degree received or currently enrolled in
  \item please give the degree, institution name, institution city, institute state/province, and date (or expected date)
  \item List electives that you've taken, you're taking this semester, and you're planning to take next semester. 
\end{itemize}





\section{ Experience}
\subsectionnoit{\textbf{AA BB Innovation}}{Shenzhen, China}
\role{Research Intern} {} {Feb -- Mar, 2019}
\begin{itemize}
  \item Work experience: include the company's name and a 1-2 sentence description of your duties.
  \item Projects: describe projects you've completed (through coursework, extra-curricular activities, and personal efforts)
  \item what your contributions were, and give pointers to project Web sites and/or software releases.
\end{itemize}

\subsectionnoit{\textbf{AA BB Instruments}}{YYY, XXX}
\role{Research Intern} {} {Feb -- Mar, 2019}
\begin{itemize}
  \item Work experience: include the company's name and a 1-2 sentence description of your duties.
  \item Projects: describe projects you've completed (through coursework, extra-curricular activities, and personal efforts)
  \item what your contributions were, and give pointers to project Web sites and/or software releases.
\end{itemize}


\section{ Honors and Awards}
\datedline{Outstanding Bachelor Thesis of Southeast University (top 250\%)}{Jun, 2019}
\datedline{XXX Electric Scholorship}{Apr, 2019}
\datedline{\textit{\nth{1} Place}, XX Contest of Southeast University}{Oct, 2018}
\datedline{\textit{\nth{1} Prize}, XX Contest for Undergraduates}{Oct, 2017}
\datedline{\textit{\nth{1} Prize}, XXX Contest of China}{Jun, 2017}
\datedline{YYY Scholorship}{Nov, 2016}
\datedline{\textit{\nth{2} Prize}, AAA Sjkas Competition}{Oct, 2016}
\datedline{National Scholorship (top 100\%)}{Oct, 2016}

\section{ Skills}
\begin{itemize}[parsep=0.1ex]
  \item Programming Languages: Python, C/C++, Matlab, C\#, Perl, Java, VHDL
  \item Software and platforms: ROS, OpenCV, PyTorch, TensorFlow
  \item Languages: English - Fluent (TOEFL 121), Mandarin - Native speaker

\end{itemize}


%\section{ Miscellaneous}
%\begin{itemize}[parsep=0.5ex]
%  \item Blog: http://your.blog.me
%  \item GitHub: https://github.com/aaa
%  \item Sports: cycling, swimming
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
